Do NBA Teams Avoid Trading within Their Own Division?^[We appreciate feedback we received on this paper from Skye Bender-deMoll, Pavel Krivitsky and David Schaefer.]

### 2022-01-05 Manuscript.Rmd
Fix alpha in figure caption

```{r alphas, fig.cap="**Divisional Homophily in NBA Trades by Season.** (as computed by Moody's $\alpha$-index)."}
netlist <- lapply(graphlist, intergraph::asNetwork)
names(netlist) <- vapply(graphlist, igraph::get.graph.attribute, character(1), "season")

>>>>

```{r alphas, fig.cap="**Divisional Homophily in NBA Trades by Season.** (as computed by Moody's $\\alpha$-index)."}
netlist <- lapply(graphlist, intergraph::asNetwork)
names(netlist) <- vapply(graphlist, igraph::get.graph.attribute, character(1), "season")
